Wavelet Spatio-Temporal Change Detection on multi-temporal POLSAR images

### 2021-10-22 tex/paper.wecs/wecs_tgrs.tex
update figures in the tex

\begin{figure}[htb!]
\centering
%\includegraphics[width=40pc]{EllipsoidChanges/ellipses_all}
\includegraphics[scale=.17]{ellipses_t1}
\includegraphics[scale=.17]{ellipses_t2}
\includegraphics[scale=.17]{ellipses_t3}
\includegraphics[scale=.17]{ellipses_t4}
\caption{Synthetic multi-temporal ($n=4$) images. Features and changes come as ellipses and dots.}
\label{F:EllipsoidChanges}
\end{figure}

\begin{figure}[htp!]
\includegraphics[scale=.1]{total_changes}(a)
\includegraphics[scale=.1]{corr_changes_dm}(b)
\includegraphics[scale=.1]{corr_changes_tm}(c)
\includegraphics[scale=.1]{corr_changes_logratios}(d)
\includegraphics[scale=.1]{corr_changes_dm_nowavelets}(e)
\includegraphics[scale=.1]{corr_changes_tm_nowavelets}(f)
\caption{Synthetic images with changing ellipses. (a) Image composed by the total changes over time. 
(b) Proposed db2 WECS $\vd(m)$ with $J=2$; (c) Proposed db2 WECS $\vt(m)$ with $J=2$.
(d) Standard approach. (e) $\vd(m)$ without wavelets. (f) $\vt(m)$  without wavelets. 
}
\label{F:Changes_methods_images}
\end{figure}

@@

\begin{figure}[htp!]
\includegraphics[scale=.13]{methods_comparison}\hspace{-.5cm}(a) 
\includegraphics[scale=.13]{levels_comparison_WithReference}\hspace{-.5cm}(b)\\
\includegraphics[scale=.13]{families_comparison_WithReference}\hspace{-.5cm}(c)
\includegraphics[scale=.13]{dm_comparison_wavelet_deepL}\hspace{-.5cm}(d) \\
\includegraphics[scale=.13]{levels_comparison_NoReference}\hspace{-.5cm}(e)
\includegraphics[scale=.13]{families_comparison_NoReference}\hspace{-.5cm}(f)
\caption{ROC curves for detection of changing ellipses in synthetic images and different methods. (a) The proposed methods in black (db2 WECS $\vd(m)$) and green (db2 WECS $\vt(m)$) vs three non-wavelet methods: standard (red stars); $\vd(m)$ (blue); and $\vt(m)$ (red circles). 
(b) db2 $\vd(m)$ with different levels.
(c) $\vd(m)$ with different wavelet bases and J=2;
(d) The proposed db2 WECS $\vd(m)$ (red circles) and $\vd(m)$ with deep-learning feature extraction and without wavelets (yellow line).  
(e) db2 $\vt(m)$ with different levels. (f) $\vt(m)$ with different wavelet bases and J=2. }
\label{F:EllipsoidChanges_details}
\end{figure}

@@

\begin{figure}[htp!]
\includegraphics[scale=.12]{J1_VV_squared_meandev}(a)
\includegraphics[scale=.12]{consecdif_J1_VV_squared_meandev}(b)\\
\includegraphics[scale=.12]{J2_VV_squared_meandev}(c)
\includegraphics[scale=.12]{consecdif_J2_VV_squared_meandev}(d)\\
\includegraphics[scale=.12]{J3_VV_squared_meandev}(e)
\includegraphics[scale=.12]{consecdif_J3_VV_squared_meandev}(f)\\
\includegraphics[scale=.12]{J4_VV_squared_meandev}(g)
\includegraphics[scale=.12]{consecdif_J4_VV_squared_meandev}(h)
\caption{{\sc VV Polarization Channel} Series of squared deviations $\vd(m)$ and $\vt(m)$. The red horizontal line represents the median value and the yellow horizontal line represents their median plus two times their absolute median deviation.  $\vd(m)$ - Approximation Levels:  (a) $J=1$; (c) $J=2$; (e) $J=3$; (g) $J=4$. $\vt(m)$ - Approximation Levels:  (b) $J=1$; (d) $J=2$; (f) $J=3$; (h) $J=4$. 
}
\label{F:squared_J1-4_VV}
\end{figure}

\begin{figure}[htp!]
\includegraphics[scale=.12]{J1_VH_squared_meandev}(a)
\includegraphics[scale=.12]{consecdif_J1_VH_squared_meandev}(b)\\
\includegraphics[scale=.12]{J2_VH_squared_meandev}(c)
\includegraphics[scale=.12]{consecdif_J2_VH_squared_meandev}(d)\\
\includegraphics[scale=.12]{J3_VH_squared_meandev}(e)
\includegraphics[scale=.12]{consecdif_J3_VH_squared_meandev}(f)\\
\includegraphics[scale=.12]{J4_VH_squared_meandev}(g)
\includegraphics[scale=.12]{consecdif_J4_VH_squared_meandev}(h)
\caption{{\sc VH Polarization  Channel} Series of squared deviations $\vd(m)$ and $\vt(m)$. The red horizontal line represents the median value and the yellow horizontal line represents their median plus two times their absolute median deviation.  $\vd(m)$ - Approximation Levels:  (a) $J=1$; (c) $J=2$; (e) $J=3$; (g) $J=4$. $\vt(m)$ - Approximation Levels:  (b) $J=1$; (d) $J=2$; (f) $J=3$; (h) $J=4$. 
}
\label{F:squared_J1-4_VH}
\end{figure}

\begin{figure}[htp!]
\includegraphics[scale=.12]{J1_euclid_squared_meandev}(a)
\includegraphics[scale=.12]{consecdif_J1_euclid_squared_meandev}(b)\\
\includegraphics[scale=.12]{J2_euclid_squared_meandev}(c)
\includegraphics[scale=.12]{consecdif_J2_euclid_squared_meandev}(d)\\
\includegraphics[scale=.12]{J3_euclid_squared_meandev}(e)
\includegraphics[scale=.12]{consecdif_J3_euclid_squared_meandev}(f)\\
\includegraphics[scale=.12]{J4_euclid_squared_meandev}(g)
\includegraphics[scale=.12]{consecdif_J4_euclid_squared_meandev}(h)
\caption{{\sc Combined Channels} Series of squared deviations $\vd(m)$ and $\vt(m)$. The red horizontal line represents the median value  and the yellow horizontal line represents their median plus two times their absolute median deviation.  $\vd(m)$ - Approximation Levels:  (a) $J=1$; (c) $J=2$; (e) $J=3$; (g) $J=4$. $\vt(m)$ - Approximation Levels:  (b) $J=1$; (d) $J=2$; (f) $J=3$; (h) $J=4$. 
}
\label{F:squared_J1-4_euclid}
\end{figure}

\begin{figure}[htp!]
\includegraphics[scale=.12]{J3_VV_squared_meandev}(a)
\includegraphics[scale=.12]{consecdif_J3_VV_squared_meandev}(b)\\
\includegraphics[scale=.12]{J3_VV_sqrdif_change_locations}(c)
\includegraphics[scale=.12]{consecdif_J3_VV_sqrdif_change_locations}(d)\\
\includegraphics[scale=.12]{J3_VV_sqrdif_lowest_cor_locations}(e)
\includegraphics[scale=.12]{consecdif_J3_VV_sqrdif_lowest_cor_locations}(f)\\
\includegraphics[scale=.12]{perc01_J3_VV_sqrdif_change_locations}(g)
\includegraphics[scale=.12]{perc01_consecdif_J3_VV_sqrdif_change_locations}(h)\\
\includegraphics[scale=.12]{perc01_J3_VV_sqrdif_lowest_cor_locations}(i)
\includegraphics[scale=.12]{perc01_consecdif_J3_VV_sqrdif_lowest_cor_locations}(j)
\caption{{\sc VV Polarization Channel} Series of squared mean deviations at level $J=3$: (a) $\vd(m)$; (b) $\vt(m)$. Red horizontal line represents the median value and yellow line represents two absolute median deviations beyond the median. Squared approximation coefficient deviations: 0.1\% highest absolute correlations - (c) $\vd(m)$;  (d) $\vt(m)$; 0.1\% smallest absolute correlations - (e) $\vd(m)$; (f) $\vt(m)$; 0.01\% highest absolute correlations - (g) $\vd(m)$;  (h) $\vt(m)$;  0.01\% smallest absolute correlations - (i) $\vd(m)$; (j)  $\vt(m)$. 
}  
\label{F:squared_meandev_J3_VV}
\end{figure}

\begin{figure}[htp!]
\includegraphics[scale=.12]{J3_VH_squared_meandev}(a)
\includegraphics[scale=.12]{consecdif_J3_VH_squared_meandev}(b)

\includegraphics[scale=.12]{J3_VH_sqrdif_change_locations}(c)
\includegraphics[scale=.12]{consecdif_J3_VH_sqrdif_change_locations}(d)

\includegraphics[scale=.12]{J3_VH_sqrdif_lowest_cor_locations}(e)
\includegraphics[scale=.12]{consecdif_J3_VH_sqrdif_lowest_cor_locations}(f)

\includegraphics[scale=.12]{perc01_J3_VH_sqrdif_change_locations}(g)
\includegraphics[scale=.12]{perc01_consecdif_J3_VH_sqrdif_change_locations}(h)

\includegraphics[scale=.12]{perc01_J3_VH_sqrdif_lowest_cor_locations}(i)
\includegraphics[scale=.12]{perc01_consecdif_J3_VH_sqrdif_lowest_cor_locations}(j)

@@

\begin{figure}[htp!]
\includegraphics[scale=.12]{J3_euclid_squared_meandev}(a)
\includegraphics[scale=.12]{consecdif_J3_euclid_squared_meandev}(b)\\
\includegraphics[scale=.12]{J3_euclid_sqrdif_change_locations}(c)
\includegraphics[scale=.12]{consecdif_J3_euclid_sqrdif_change_locations}(d)\\
\includegraphics[scale=.12]{J3_euclid_sqrdif_lowest_cor_locations}(e)
\includegraphics[scale=.12]{consecdif_J3_euclid_sqrdif_lowest_cor_locations}(f)\\
\includegraphics[scale=.12]{perc01_J3_euclid_sqrdif_change_locations}(g)
\includegraphics[scale=.12]{perc01_consecdif_J3_euclid_sqrdif_change_locations}(h)\\
\includegraphics[scale=.12]{perc01_J3_euclid_sqrdif_lowest_cor_locations}(i)
\includegraphics[scale=.12]{perc01_consecdif_J3_euclid_sqrdif_lowest_cor_locations}(j)
\caption{{\sc Combined Channels} Series of squared mean deviations at level $J=3$: (a) $\vd(m)$; (b) $\vt(m)$. Red horizontal line represents the median value and yellow line represents two absolute median deviations beyond the median. Squared approximation coefficient deviations: 0.1\% highest absolute correlations - (c) $\vd(m)$;  (d) $\vt(m)$; 0.1\% smallest absolute correlations - (e) $\vd(m)$; (f) $\vt(m)$; 0.01\% highest absolute correlations - (g) $\vd(m)$;  (h) $\vt(m)$;  0.01\% smallest absolute correlations - (i) $\vd(m)$; (j)  $\vt(m)$. 
} 
\label{F:squared_meandev_J3_euclid}
\end{figure}

@@

\begin{figure}[htp!]
\includegraphics[scale=.12]{J2_VV_image_cor}(a)
\includegraphics[scale=.12]{J2_VH_image_cor}(b)\\
\includegraphics[scale=.12]{J2_euclid_image_cor}(c)
\includegraphics[scale=.12]{J3_VV_image_cor}(d)\\ 
\includegraphics[scale=.12]{J3_VH_image_cor}(e)
\includegraphics[scale=.12]{J3_euclid_image_cor}(f)

@@

\begin{figure}[htp!]
\includegraphics[scale=.12]{consecdif_J2_VV_image_cor}(a)
\includegraphics[scale=.12]{consecdif_J2_VH_image_cor}(b)\\
\includegraphics[scale=.12]{consecdif_J2_euclid_image_cor}(c)
\includegraphics[scale=.12]{consecdif_J3_VV_image_cor}(d)\\ 
\includegraphics[scale=.12]{consecdif_J3_VH_image_cor}(e)
\includegraphics[scale=.12]{consecdif_J3_euclid_image_cor}(f)

>>>>

\begin{figure}[htb!]
\centering
%\includegraphics[width=40pc]{EllipsoidChanges/ellipses_all}
\includegraphics[scale=.17]{../../figs/ellipses_t1}
\includegraphics[scale=.17]{../../figs/ellipses_t2}
\includegraphics[scale=.17]{../../figs/ellipses_t3}
\includegraphics[scale=.17]{../../figs/ellipses_t4}
\caption{Synthetic multi-temporal ($n=4$) images. Features and changes come as ellipses and dots.}
\label{F:EllipsoidChanges}
\end{figure}

\begin{figure}[htp!]
\includegraphics[scale=.1]{../../figs/total_changes}(a)
\includegraphics[scale=.1]{../../figs/corr_changes_dm}(b)
\includegraphics[scale=.1]{../../figs/corr_changes_tm}(c)
\includegraphics[scale=.1]{../../figs/corr_changes_logratios}(d)
\includegraphics[scale=.1]{../../figs/corr_changes_dm_nowavelets}(e)
\includegraphics[scale=.1]{../../figs/corr_changes_tm_nowavelets}(f)
\caption{Synthetic images with changing ellipses. (a) Image composed by the total changes over time. 
(b) Proposed db2 WECS $\vd(m)$ with $J=2$; (c) Proposed db2 WECS $\vt(m)$ with $J=2$.
(d) Standard approach. (e) $\vd(m)$ without wavelets. (f) $\vt(m)$  without wavelets. 
}
\label{F:Changes_methods_images}
\end{figure}

@@

\begin{figure}[htp!]
\includegraphics[scale=.13]{../../figs/methods_comparison}\hspace{-.5cm}(a) 
\includegraphics[scale=.13]{../../figs/levels_comparison_WithReference}\hspace{-.5cm}(b)\\
\includegraphics[scale=.13]{../../figs/families_comparison_WithReference}\hspace{-.5cm}(c)
\includegraphics[scale=.13]{../../figs/dm_comparison_wavelet_deepL}\hspace{-.5cm}(d) \\
\includegraphics[scale=.13]{../../figs/levels_comparison_NoReference}\hspace{-.5cm}(e)
\includegraphics[scale=.13]{../../figs/families_comparison_NoReference}\hspace{-.5cm}(f)
\caption{ROC curves for detection of changing ellipses in synthetic images and different methods. (a) The proposed methods in black (db2 WECS $\vd(m)$) and green (db2 WECS $\vt(m)$) vs three non-wavelet methods: standard (red stars); $\vd(m)$ (blue); and $\vt(m)$ (red circles). 
(b) db2 $\vd(m)$ with different levels.
(c) $\vd(m)$ with different wavelet bases and J=2;
(d) The proposed db2 WECS $\vd(m)$ (red circles) and $\vd(m)$ with deep-learning feature extraction and without wavelets (yellow line).  
(e) db2 $\vt(m)$ with different levels. (f) $\vt(m)$ with different wavelet bases and J=2. }
\label{F:EllipsoidChanges_details}
\end{figure}

@@

\begin{figure}[htp!]
\includegraphics[scale=.12]{../../figs/J1_VV_squared_meandev}(a)
\includegraphics[scale=.12]{../../figs/consecdif_J1_VV_squared_meandev}(b)\\
\includegraphics[scale=.12]{../../figs/J2_VV_squared_meandev}(c)
\includegraphics[scale=.12]{../../figs/consecdif_J2_VV_squared_meandev}(d)\\
\includegraphics[scale=.12]{../../figs/J3_VV_squared_meandev}(e)
\includegraphics[scale=.12]{../../figs/consecdif_J3_VV_squared_meandev}(f)\\
\includegraphics[scale=.12]{../../figs/J4_VV_squared_meandev}(g)
\includegraphics[scale=.12]{../../figs/consecdif_J4_VV_squared_meandev}(h)
\caption{{\sc VV Polarization Channel} Series of squared deviations $\vd(m)$ and $\vt(m)$. The red horizontal line represents the median value and the yellow horizontal line represents their median plus two times their absolute median deviation.  $\vd(m)$ - Approximation Levels:  (a) $J=1$; (c) $J=2$; (e) $J=3$; (g) $J=4$. $\vt(m)$ - Approximation Levels:  (b) $J=1$; (d) $J=2$; (f) $J=3$; (h) $J=4$. 
}
\label{F:squared_J1-4_VV}
\end{figure}

\begin{figure}[htp!]
\includegraphics[scale=.12]{../../figs/J1_VH_squared_meandev}(a)
\includegraphics[scale=.12]{../../figs/consecdif_J1_VH_squared_meandev}(b)\\
\includegraphics[scale=.12]{../../figs/J2_VH_squared_meandev}(c)
\includegraphics[scale=.12]{../../figs/consecdif_J2_VH_squared_meandev}(d)\\
\includegraphics[scale=.12]{../../figs/J3_VH_squared_meandev}(e)
\includegraphics[scale=.12]{../../figs/consecdif_J3_VH_squared_meandev}(f)\\
\includegraphics[scale=.12]{../../figs/J4_VH_squared_meandev}(g)
\includegraphics[scale=.12]{../../figs/consecdif_J4_VH_squared_meandev}(h)
\caption{{\sc VH Polarization  Channel} Series of squared deviations $\vd(m)$ and $\vt(m)$. The red horizontal line represents the median value and the yellow horizontal line represents their median plus two times their absolute median deviation.  $\vd(m)$ - Approximation Levels:  (a) $J=1$; (c) $J=2$; (e) $J=3$; (g) $J=4$. $\vt(m)$ - Approximation Levels:  (b) $J=1$; (d) $J=2$; (f) $J=3$; (h) $J=4$. 
}
\label{F:squared_J1-4_VH}
\end{figure}

\begin{figure}[htp!]
\includegraphics[scale=.12]{../../figs/J1_euclid_squared_meandev}(a)
\includegraphics[scale=.12]{../../figs/consecdif_J1_euclid_squared_meandev}(b)\\
\includegraphics[scale=.12]{../../figs/J2_euclid_squared_meandev}(c)
\includegraphics[scale=.12]{../../figs/consecdif_J2_euclid_squared_meandev}(d)\\
\includegraphics[scale=.12]{../../figs/J3_euclid_squared_meandev}(e)
\includegraphics[scale=.12]{../../figs/consecdif_J3_euclid_squared_meandev}(f)\\
\includegraphics[scale=.12]{../../figs/J4_euclid_squared_meandev}(g)
\includegraphics[scale=.12]{../../figs/consecdif_J4_euclid_squared_meandev}(h)
\caption{{\sc Combined Channels} Series of squared deviations $\vd(m)$ and $\vt(m)$. The red horizontal line represents the median value  and the yellow horizontal line represents their median plus two times their absolute median deviation.  $\vd(m)$ - Approximation Levels:  (a) $J=1$; (c) $J=2$; (e) $J=3$; (g) $J=4$. $\vt(m)$ - Approximation Levels:  (b) $J=1$; (d) $J=2$; (f) $J=3$; (h) $J=4$. 
}
\label{F:squared_J1-4_euclid}
\end{figure}

\begin{figure}[htp!]
\includegraphics[scale=.12]{../../figs/J3_VV_squared_meandev}(a)
\includegraphics[scale=.12]{../../figs/consecdif_J3_VV_squared_meandev}(b)\\
\includegraphics[scale=.12]{../../figs/J3_VV_sqrdif_change_locations}(c)
\includegraphics[scale=.12]{../../figs/consecdif_J3_VV_sqrdif_change_locations}(d)\\
\includegraphics[scale=.12]{../../figs/J3_VV_sqrdif_lowest_cor_locations}(e)
\includegraphics[scale=.12]{../../figs/consecdif_J3_VV_sqrdif_lowest_cor_locations}(f)\\
\includegraphics[scale=.12]{../../figs/perc01_J3_VV_sqrdif_change_locations}(g)
\includegraphics[scale=.12]{../../figs/perc01_consecdif_J3_VV_sqrdif_change_locations}(h)\\
\includegraphics[scale=.12]{../../figs/perc01_J3_VV_sqrdif_lowest_cor_locations}(i)
\includegraphics[scale=.12]{../../figs/perc01_consecdif_J3_VV_sqrdif_lowest_cor_locations}(j)
\caption{{\sc VV Polarization Channel} Series of squared mean deviations at level $J=3$: (a) $\vd(m)$; (b) $\vt(m)$. Red horizontal line represents the median value and yellow line represents two absolute median deviations beyond the median. Squared approximation coefficient deviations: 0.1\% highest absolute correlations - (c) $\vd(m)$;  (d) $\vt(m)$; 0.1\% smallest absolute correlations - (e) $\vd(m)$; (f) $\vt(m)$; 0.01\% highest absolute correlations - (g) $\vd(m)$;  (h) $\vt(m)$;  0.01\% smallest absolute correlations - (i) $\vd(m)$; (j)  $\vt(m)$. 
}  
\label{F:squared_meandev_J3_VV}
\end{figure}

\begin{figure}[htp!]
\includegraphics[scale=.12]{../../figs/J3_VH_squared_meandev}(a)
\includegraphics[scale=.12]{../../figs/consecdif_J3_VH_squared_meandev}(b)

\includegraphics[scale=.12]{../../figs/J3_VH_sqrdif_change_locations}(c)
\includegraphics[scale=.12]{../../figs/consecdif_J3_VH_sqrdif_change_locations}(d)

\includegraphics[scale=.12]{../../figs/J3_VH_sqrdif_lowest_cor_locations}(e)
\includegraphics[scale=.12]{../../figs/consecdif_J3_VH_sqrdif_lowest_cor_locations}(f)

\includegraphics[scale=.12]{../../figs/perc01_J3_VH_sqrdif_change_locations}(g)
\includegraphics[scale=.12]{../../figs/perc01_consecdif_J3_VH_sqrdif_change_locations}(h)

\includegraphics[scale=.12]{../../figs/perc01_J3_VH_sqrdif_lowest_cor_locations}(i)
\includegraphics[scale=.12]{../../figs/perc01_consecdif_J3_VH_sqrdif_lowest_cor_locations}(j)

@@

\begin{figure}[htp!]
\includegraphics[scale=.12]{../../figs/J3_euclid_squared_meandev}(a)
\includegraphics[scale=.12]{../../figs/consecdif_J3_euclid_squared_meandev}(b)\\
\includegraphics[scale=.12]{../../figs/J3_euclid_sqrdif_change_locations}(c)
\includegraphics[scale=.12]{../../figs/consecdif_J3_euclid_sqrdif_change_locations}(d)\\
\includegraphics[scale=.12]{../../figs/J3_euclid_sqrdif_lowest_cor_locations}(e)
\includegraphics[scale=.12]{../../figs/consecdif_J3_euclid_sqrdif_lowest_cor_locations}(f)\\
\includegraphics[scale=.12]{../../figs/perc01_J3_euclid_sqrdif_change_locations}(g)
\includegraphics[scale=.12]{../../figs/perc01_consecdif_J3_euclid_sqrdif_change_locations}(h)\\
\includegraphics[scale=.12]{../../figs/perc01_J3_euclid_sqrdif_lowest_cor_locations}(i)
\includegraphics[scale=.12]{../../figs/perc01_consecdif_J3_euclid_sqrdif_lowest_cor_locations}(j)
\caption{{\sc Combined Channels} Series of squared mean deviations at level $J=3$: (a) $\vd(m)$; (b) $\vt(m)$. Red horizontal line represents the median value and yellow line represents two absolute median deviations beyond the median. Squared approximation coefficient deviations: 0.1\% highest absolute correlations - (c) $\vd(m)$;  (d) $\vt(m)$; 0.1\% smallest absolute correlations - (e) $\vd(m)$; (f) $\vt(m)$; 0.01\% highest absolute correlations - (g) $\vd(m)$;  (h) $\vt(m)$;  0.01\% smallest absolute correlations - (i) $\vd(m)$; (j)  $\vt(m)$. 
} 
\label{F:squared_meandev_J3_euclid}
\end{figure}

@@

\begin{figure}[htp!]
\includegraphics[scale=.12]{../../figs/J2_VV_image_cor}(a)
\includegraphics[scale=.12]{../../figs/J2_VH_image_cor}(b)\\
\includegraphics[scale=.12]{../../figs/J2_euclid_image_cor}(c)
\includegraphics[scale=.12]{../../figs/J3_VV_image_cor}(d)\\ 
\includegraphics[scale=.12]{../../figs/J3_VH_image_cor}(e)
\includegraphics[scale=.12]{../../figs/J3_euclid_image_cor}(f)

@@

\begin{figure}[htp!]
\includegraphics[scale=.12]{../../figs/consecdif_J2_VV_image_cor}(a)
\includegraphics[scale=.12]{../../figs/consecdif_J2_VH_image_cor}(b)\\
\includegraphics[scale=.12]{../../figs/consecdif_J2_euclid_image_cor}(c)
\includegraphics[scale=.12]{../../figs/consecdif_J3_VV_image_cor}(d)\\ 
\includegraphics[scale=.12]{../../figs/consecdif_J3_VH_image_cor}(e)
\includegraphics[scale=.12]{../../figs/consecdif_J3_euclid_image_cor}(f)
